\documentclass{academic-cv}

\begin{document}

% CV Header
% Usage: \cvheader{first_name}{last_name}{address}{email}{linkedin (placeholder ok)}{github (placeholder ok)}{website (placeholder ok)}
% All slots except email can show placeholder text while still being clickable with actual URLs.
\cvheader{John}{Doe}{123 Ave, SL, CA}{%
    \emaillink{john.doe@university.edu}% clickable email
}{%
    \linkedinplaceholder{LinkedIn}{johndoe}% clickable placeholder
}{%
    \githubplaceholder{GitHub}{johndoe}% clickable placeholder
}{%
    \websiteplaceholder{Website}{johndoe.com}% clickable placeholder
}

% Education Section
\cvsection{Education}

\cvitem{Ph.D. in Computer Science}{2020 -- 2024}{University of Excellence}{%
    Dissertation: ``Advanced Machine Learning Techniques for Natural Language Processing''\\
    Advisor: Dr. Jane Smith\\
    GPA: 3.9/4.0
}

\cvitem{M.S. in Computer Science}{2018 -- 2020}{University of Excellence}{%
    Thesis: ``Deep Learning Applications in Computer Vision''\\
    GPA: 3.8/4.0
}

\cvitem{B.S. in Computer Science}{2014 -- 2018}{State University}{%
    Magna Cum Laude, Phi Beta Kappa\\
    GPA: 3.7/4.0
}

% Research Experience
\cvsection{Research Experience}

\cvitem{Research Assistant}{2020 -- 2024}{Machine Learning Lab, University of Excellence}{%
    \begin{cvlist}
        \item Developed novel algorithms for natural language understanding
        \item Published 5 papers in top-tier conferences (ACL, EMNLP, ICML)
        \item Mentored 3 undergraduate research students
        \item Collaborated with industry partners on applied research projects
    \end{cvlist}
}

\cvitem{Summer Research Intern}{Summer 2019}{Tech Giants Research Lab}{%
    \begin{cvlist}
        \item Worked on large-scale distributed machine learning systems
        \item Implemented and optimized neural network architectures
        \item Contributed to open-source machine learning frameworks
    \end{cvlist}
}

% Publications
\cvsection{Publications}

\cvsubsection{Conference Papers}

\cvsimpleitem{Doe, J., Smith, J. (2024). ``Advanced Techniques in Neural Language Models.'' \textit{Proceedings of ACL 2024}. pp. 123-135.}{}

\cvsimpleitem{Doe, J., Johnson, A., Smith, J. (2023). ``Efficient Training of Large Language Models.'' \textit{Proceedings of EMNLP 2023}. pp. 456-470.}{}

\cvsimpleitem{Doe, J., Brown, K. (2023). ``Cross-lingual Transfer Learning for Low-Resource Languages.'' \textit{Proceedings of ICML 2023}. pp. 789-802.}{}

\cvsubsection{Journal Papers}

\cvsimpleitem{Doe, J., Smith, J., Wilson, R. (2024). ``A Comprehensive Survey of Transformer Architectures.'' \textit{Journal of Machine Learning Research}, 25(1), 1-45.}{}

% Teaching Experience
\cvsection{Teaching Experience}

\cvitem{Teaching Assistant}{Fall 2021, Spring 2022}{CS 101: Introduction to Computer Science}{%
    \begin{cvlist}
        \item Conducted weekly lab sessions for 50+ students
        \item Graded assignments and provided detailed feedback
        \item Held office hours and provided one-on-one tutoring
        \item Received excellent teaching evaluations (4.8/5.0)
    \end{cvlist}
}

\cvitem{Guest Lecturer}{Spring 2023}{CS 701: Advanced Machine Learning}{%
    \begin{cvlist}
        \item Delivered lectures on transformer architectures and attention mechanisms
        \item Designed and graded midterm examination
        \item Mentored final projects for graduate students
    \end{cvlist}
}

% Awards and Honors
\cvsection{Awards and Honors}

\cvsimpleitem{Outstanding Graduate Student Award}{2024}
\cvsimpleitem{Best Paper Award, EMNLP 2023}{2023}
\cvsimpleitem{University Fellowship}{2020-2024}
\cvsimpleitem{Phi Beta Kappa}{2018}
\cvsimpleitem{Dean's List}{2016-2018}

% Skills
\cvsection{Technical Skills}

\cvsubsection{Programming Languages}
Python, Java, C++, R, JavaScript, SQL

\cvsubsection{Machine Learning Frameworks}
PyTorch, TensorFlow, Scikit-learn, Hugging Face Transformers

\cvsubsection{Tools and Technologies}
Git, Docker, Kubernetes, AWS, Google Cloud Platform, LaTeX

% Professional Service
\cvsection{Professional Service}

\cvsubsection{Reviewer}
\begin{cvlist}
    \item Association for Computational Linguistics (ACL) 2023, 2024
    \item Conference on Empirical Methods in Natural Language Processing (EMNLP) 2022, 2023
    \item International Conference on Machine Learning (ICML) 2023, 2024
\end{cvlist}

\cvsubsection{Organizing Committee}
\begin{cvlist}
    \item Student Volunteer Coordinator, ACL 2023
    \item Publicity Chair, Graduate Student Conference 2022
\end{cvlist}

\end{document}
